The search for long-period transiting planets in the \kepler\ light curves

### 2015-03-08 document/ms.tex
first draft of abstract

\title{%
    The search for single transit events in the \kepler\ data
}

@@

>>>>

\title{%
    The search for long-period transiting planets in the \kepler\ light curves
}

@@

Many of the most dynamically interesting planets will be on orbits longer
than the baseline of existing transit surveys (\kepler, \KT).
Future surveys (\TESS, PLATO?) will have such a short continuous coverage that
even habitable zone planets around M-dwarfs will only present a single transit
signal.
Searches for these transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each month of photometry, we train a random forest classifier on a large
number of simulated signals injected into the photometry of the same star at
different times.
Then, the model's prediction as a function of transit time is evaluated and
times above a threshold probability---chosen for each star to yield a sample
with $\sim99$~percent purity---are given as candidate transits.
Each candidate must then pass a final round of vetting including BLAH BLAH
BLAH.
Applied to every light curve in the \kepler\ archive this method yields a
list of XXXX long-period transiting planet candidates.
Using an informative prior on their eccentricities, we derive weak constraints
on the orbital periods of the candidates and demonstrate that this puts an
upper limit of ZZZZ on the occurrence rate of these planets.
